Playing Games: A Case Study in Active Learning Applied to Game Theory

### 2015-06-29 paper/paper.tex
Adding summary of approach - need discussion about participation

\begin{equation}
    (\text{Second guess}) = .33\times(\text{First guess}) + 0.20
    \label{eq:linear_relationship}
\end{equation}

@@

>>>>

\begin{equation}
    (\text{Second guess}) = .33\times(\text{First guess}) + 0.20
    \label{eq:linear_relationship_for_increasing_guesses}
\end{equation}

@@

To summarise this activity:

\begin{enumerate}
    \item Participants are explained the rules and play one round of the two
        thirds of the average game.
    \item A rationalisation and explanation of equilibrium behaviour is
        described.
    \item Participants play another round.
    \item Results are analysed and discussed.
\end{enumerate}

This activity is still quite passive in terms of physical activity (participants are
seated throughout). Nevertheless it allows the data used for the discussion of
the theory to come directly from the participants.
